Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-06-08 paper.tex
More table action.

% Load packages
\usepackage{cite} % Make references as [1-4], not [1,2,3,4]
\usepackage{url}  % Formatting web addresses
\usepackage{ifthen}  % Conditional
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
\usepackage{lscape} % Landscape orientation for tables
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
%%\begin{landscape}
  \subsection*{Table 1 - Blue Obelisk Open Source software projects}
    (Description if necessary XXXXXXXXXXXXXXX. Add citations to project names.)
      %% GeoffH - I think we should do this as multi-line, with the
      %% website below the Name
    \par \mbox{}
    \par
    \mbox{
     \begin{tabular}{|c|c|c|}
       \hline \textbf{Name} & \textbf{Website}  \\ \hline
        \multicolumn{2}{|c|}{\textbf{CML Tools}} \\ \hline
		\textbf{JUMBO} & http://sourceforge.net/projects/cml/ \\ \hline
		\textbf{CMLXOM} & https://bitbucket.org/wwmm/cmlxom/ \\ \hline
		\multicolumn{2}{|c|}{\textbf{Cheminformatics Toolkits}} \\ \hline
        \textbf{Chemistry Development Kit (CDK)} \cite{Steinbeck2003, Steinbeck2006} & http://cdk.sf.net \\ \hline
        \textbf{Cinfony} & http://cinfony.googlecode.com \\ \hline
        \textbf{Indigo} & http://ggasoftware.com/opensource/indigo \\ \hline
        \textbf{Open Babel} & http://openbabel.org \\ \hline
        \textbf{RDKit} & http://rdkit.org \\ \hline
        \multicolumn{2}{|c|}{\textbf{Second Generation}} \\ \hline
        \textbf{Avogadro} & http://avogadro.openmolecules.net \\ \hline
        \multicolumn{2}{|c|}{\textbf{Web Applications}} \\ \hline
        \textbf{ChemDoodle Web Components} & http://web.chemdoodle.com \\ \hline
        \textbf{Jmol} & http://jmol.org \\ \hline
       \multicolumn{2}{|c|}{\textbf{Integration}} \\ \hline
        \textbf{CDK-Taverna} \cite{Kuhn:2010p4001} & http://cdktaverna.wordpress.com \\ \hline
		\textbf{Lensfield2} & https://bitbucket.org/sea36/lensfield2/ \\ \hline
        \multicolumn{2}{|c|}{\textbf{Interconversion}} \\ \hline
        \textbf{OSRA} & http://osra.sf.net \\ \hline
        \textbf{OPSIN} & http://opsin.ch.cam.ac.uk \\ \hline
		\textbf{JUMBO-Converters} & https://bitbucket.org/wwmm/jumbo-converters/ \\ \hline
		\textbf{CIFXOM} \cite{DayEtAl2011} & https://bitbucket.org/wwmm/cifxom/  \\ \hline
        \multicolumn{2}{|c|}{\textbf{Structure Databases}} \\ \hline
        \textbf{Bingo}  & http://XXX.XXX.XXX \\ \hline
        \textbf{MyChem}  & http://XXX.sf.net \\ \hline
        \textbf{OrChem} \cite{RijnbeekS10} & http://orchem.sf.net \\ \hline
        \textbf{PGChem}  & http://XXX.sf.net \\ \hline
 	    \textbf{Chempound (Chem\#)} & https://bitbucket.org/chempound \\ \hline
	   \multicolumn{2}{|c|}{\textbf{Text mining}} \\ \hline
	    \textbf{OSCAR4} & https://bitbucket.org/wwmm/oscar4/ \\ \hline
		\textbf{ChemicalTagger} \cite{HawizyEtAl2011} & http://chemicaltagger.ch.cam.ac.uk/ \\ \hline
       \multicolumn{2}{|c|}{\textbf{Other}} \\ \hline
        \textbf{cclib}  & http://cclib.sf.net \\
        \hline
%% GaussSum, QMForge
       \end{tabular}
      }
%%\end{landscape}

>>>>

% Load packages
\usepackage{cite} % Make references as [1-4], not [1,2,3,4]
\usepackage{url}  % Formatting web addresses
\usepackage{ifthen}  % Conditional
\usepackage{multicol}   %Columns
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\urlstyle{rm}

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - Blue Obelisk Open Source Software projects}
    \par \mbox{}
    \par
    \mbox{
     \begin{tabular}{|c|c|c|}
       \hline \textbf{Name} & \textbf{Website}  \\ \hline
        \multicolumn{2}{|c|}{\textbf{CML Tools}} \\ \hline
        \textbf{CMLXOM} & https://bitbucket.org/wwmm/cmlxom/ \\ \hline
        \textbf{JUMBO} & http://sourceforge.net/projects/cml/ \\ \hline
        \multicolumn{2}{|c|}{\textbf{Cheminformatics Toolkits}} \\ \hline
        \textbf{Chemistry Development Kit (CDK)} \cite{Steinbeck2003, Steinbeck2006} & http://cdk.sf.net \\ \hline
        \textbf{Cinfony} & http://cinfony.googlecode.com \\ \hline
        \textbf{Indigo} & http://ggasoftware.com/opensource/indigo \\ \hline
        \textbf{Open Babel} & http://openbabel.org \\ \hline
        \textbf{RDKit} & http://rdkit.org \\ \hline
        \multicolumn{2}{|c|}{\textbf{Web Applications}} \\ \hline
        \textbf{ChemDoodle Web Components} & http://web.chemdoodle.com \\ \hline
        \textbf{Jmol} & http://jmol.org \\ \hline
        \multicolumn{2}{|c|}{\textbf{Integration}} \\ \hline
        \textbf{Bioclipse} & http://www.bioclipse.net \\ \hline
        \textbf{CDK-Taverna} \cite{Kuhn:2010p4001} & http://cdktaverna.wordpress.com \\ \hline
        \textbf{Lensfield2} & https://bitbucket.org/sea36/lensfield2/ \\ \hline
        \multicolumn{2}{|c|}{\textbf{Interconversion}} \\ \hline
        \textbf{CIFXOM} \cite{DayEtAl2011} & https://bitbucket.org/wwmm/cifxom/  \\ \hline
        \textbf{JUMBO-Converters} & https://bitbucket.org/wwmm/jumbo-converters/ \\ \hline
        \textbf{OPSIN} & http://opsin.ch.cam.ac.uk \\ \hline
        \textbf{OSRA} & http://osra.sf.net \\ \hline
        \multicolumn{2}{|c|}{\textbf{Structure Databases}} \\ \hline
        \textbf{Bingo}  & http://ggasoftware.com/opensource/bingo \\ \hline
        \textbf{Chempound (Chem\#)} & https://bitbucket.org/chempound \\ \hline
        \textbf{MyChem}  & http://mychem.sf.net \\ \hline
        \textbf{OrChem} \cite{RijnbeekS10} & http://orchem.sf.net \\ \hline
        \textbf{pgchem}  & http://pgfoundry.org/projects/pgchem/ \\ \hline
        \multicolumn{2}{|c|}{\textbf{Text mining}} \\ \hline
        \textbf{ChemicalTagger} \cite{HawizyEtAl2011} & http://chemicaltagger.ch.cam.ac.uk/ \\ \hline
        \textbf{OSCAR4} & https://bitbucket.org/wwmm/oscar4/ \\ \hline
        \multicolumn{2}{|c|}{\textbf{Computational Chemistry}} \\ \hline
        \textbf{Avogadro} & http://avogadro.openmolecules.net \\ \hline
        \textbf{cclib}  & http://cclib.sf.net \\ \hline
        \textbf{GaussSum}  & http://gausssum.sf.net \\ \hline
        \textbf{QMForge}  & http://qmforge.sf.net \\ \hline
        \hline
       \end{tabular}
      }
